---
title: "Future krill - products"
author: "Michael Sumner"
date: "12/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## WIP

Raw extraction scripts that produce various intermediate cache outputs. Each of these take some time to run, hence the cache-as-we go approach: 

- modis.R for chlorophyll-a
- oisst.R for sea surface temperature
- nsidc.R for sea ice
- currents.R for surface flux

Those raw extractions are then summarized appropriately for each variable. We can group sst, chlorophll-a, and ice-quantiles together as each are bulk properties identified by date and polygon. The current flux is a pairwise variable, and so is stored separately. 


Extraction summaries are detailed in 'Summary_ds.R', producing the final (currently in draft) output tables in R's binary serialization format ".rds". (These files contain a single data frame and can be read with the `readRDS()` function). 

## Data extraction

Area 48 Small-Scale Management Unit (SSMU), mean total chlorophyll, mean temperature, mean coverage of sea ice (<20%, 20-50%, 50-75%, 75-95%, >95%), surface area of water crossing the boundaries of the SSMUs.

We include the 'KD490' "Diffuse attenuation coefficient at 490 nm, KD2 algorithm", which is "m^-1" to integrate carbon from the chlorophyll-a over depth. 

## Regions

Area 48 SSMUs manually cleaned using Manifold GIS to ensure topological sense for all boundaries. The regions are stored in 'sf' simple features format, a data frame of SSMU properties and geometry. 

```{r regions}
x <- readRDS("shapes/Area_48_Krill_Domain.rds")
x$poly <- 1:nrow(x)
library(sf)
plot(x["poly"])
```

```{r dim-regions}
dim(x)
print(x)
```


We store the row number 'poly' as a polygon feature identifier, used in all data tables below. 

TODO: find shared boundary lengths between pairs of polygons: 

```{r arc}
arc <- silicate::ARC(x)
plot(arc)
```

## Chlorophyll-a and SST

Chlorophyll-a based on the Johnson 2013 algorith was calculated for 
daily L3bin RRS products for the MODISA product. These values are then aggregated into polygon averages on a monthly basis. 

The mean chlorophyll-a as well as the number of bins used is recorded. 

The KD490 "Diffuse attenuation coefficient at 490 nm, KD2 algorithm, m^-1" is also included from the monthly L3mapped products. 

Sea surface temperature from the monthly Optimally Interpolated Sea Surface Temperature product provided by NOAA. 

```{r chl-sst}
chl_sst <- readRDS("chl_sst.rds")
chl_sst
```


## Sea ice

Sea ice is quantiled area covered with percentage classes (<20%, 20-50%, 50-75%, 75-95%, >95%), from the NSIDC 25km polar monthly average product. 

Values are km^2. Note that all pixels in the sea ice product have been used, and assumed to have constant area at 25km^2. If the polygons overlaid pixels that are consided to be land or otherwise missing by the product they are set to 0 and the are was included. 

```{r ice}
ice <- readRDS("ice_area.rds")
ice
```

## Flux

Boundary flux is calculated from altimetry data products of surface currents, these are daily remote sensing grids of meridional (U) and zonal (V) components of velocity in m/s-1. The global grids are processed into [polar grid form](https://github.com/AustralianAntarcticDivision/raad-deriv#polar-currents). Cell values (U and V in m/s-1) that lie on polygon boundaries are extracted and summarized in terms of source and target polygon. 

Pairs are polygon neighbours, the row-index of the regions above. We calculate the *sum of flux magnitude* between polygons. 

```{r flux}
flux <- readRDS("flux_pairs.rds")
flux
```

TODO: shared boundary lengths between polygons



